\begin{thebibliography}{9}

% Introduction. Report from verizon. Why this subject is important.
\bibitem{verizon14}
\emph{"2014 Data Breach Investigations Report"} Verizon (2014) %http://www.verizonenterprise.com/DBIR/2014/

% Related works. 
\bibitem{chandola09}
Chandola, Varun, Arindam Banerjee, and Vipin Kumar. \emph{"Anomaly detection: A survey."} ACM Computing Surveys (CSUR) 41.3 (2009): 15.

\bibitem{aggarwal01}
Aggarwal, Charu C., and Philip S. Yu. "Outlier detection for high dimensional data." ACM Sigmod Record. Vol. 30. No. 2. ACM, 2001.

\bibitem{ramaswamy00}
Ramaswamy, Sridhar, Rajeev Rastogi, and Kyuseok Shim. "Efficient algorithms for mining outliers from large data sets." ACM SIGMOD Record. Vol. 29. No. 2. ACM, 2000.

\bibitem{breuning00}
Breunig, Markus M., et al. "LOF: identifying density-based local outliers." ACM Sigmod Record. Vol. 29. No. 2. ACM, 2000.

% Dataset. 
\bibitem{tavallaee09}
Tavallaee, Mahbod, et al. \emph{"A detailed analysis of the KDD CUP 99 data set."} Proceedings of the Second IEEE Symposium on Computational Intelligence for Security and Defence Applications 2009. 2009
\bibitem{olusola10}
Olusola, Adetunmbi A., Adeola S. Oladele, and Daramola O. Abosede. "Analysis of KDD’99 Intrusion detection dataset for selection of relevance features." Proceedings of the World Congress on Engineering and Computer Science. Vol. 1. 2010.
\bibitem{kayacik05}
Kayacik, H. Günes, A. Nur Zincir-Heywood, and Malcolm I. Heywood. "Selecting features for intrusion detection: A feature relevance analysis on KDD 99 intrusion detection datasets." Proceedings of the third annual conference on privacy, security and trust. 2005.

% methods. Spectral clustering
\bibitem{jianbo00}
Jianbo Shi and Jitendra Malik, Normalized Cuts and Image Segmen- tation IEEE Transactions on Pattern Analysis and Machine Intelligence, 22(8)(2000) 888-905.

\bibitem{ng01}
Ng, Andrew Y., Michael I. Jordan, and Yair Weiss. "On spectral clustering: Analysis and an algorithm." Advances in neural information processing systems 2 (2002): 849-856.

\bibitem{jordan04}
Jordan, Francis R. Bach Michael I., and F. R. Bach. "Learning spectral clustering." Advances in Neural Information Processing Systems 16 (2004): 305-312.

\bibitem{dhillon04}
Dhillon, Inderjit S. and Guan, Yuqiang and Kulis, Brian, Kernel K-means, Spectral Clustering and Normalized Cuts, In Proceedings of the tenth ACM SIGKDD International conference on Knowledge discovery and data mining (KDD’04),(2004) 551-556.

\bibitem{cding04}
C.Ding and X. He. Linearized Cluster Assignment via Spectral Ordering, In proceedings of International Conference on Machine Learning, New York 2004.

\bibitem{ulrike07}
Von Luxburg, Ulrike. "A tutorial on spectral clustering." Statistics and computing 17.4 (2007): 395-416.

% methods. Outlier detection.
\bibitem{knorr00}
Knorr, Edwin M., Raymond T. Ng, and Vladimir Tucakov. "Distance-based outliers: algorithms and applications." The VLDB Journal—The International Journal on Very Large Data Bases 8.3-4 (2000): 237-253.

\end{thebibliography}
